### 2022-03-21 paper/ase22/approach.tex

The \emph{syntax-based \sent expansion} phase expands the seed
\sents with additional syntactic elements (i.e., words
\sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
syntactic structures ({\bf G2}). It first performs a syntax analysis
to identify the part-of-speech (PoS) tags that can be inserted to each
seed, by comparing the PoS parse trees between the seed \sent and
many other \sents from a large reference dataset. Each identified
tag is inserted into the seed as a \emph{mask}. It then uses an NLP
recommendation model (i.e., BERT \cite{}) to suggest possible
words. If a resulting \sent is validated to be consistent with the
specification which additionally defines the rules for expansion
(e.g., the expanded word should be \neu), {\bf G3} and {\bf G4} are
still satisfied.  Last, because some validated \sents may include
unacceptable suggested words given the context \sw{is this the
  right motivation to do selection?} \jl{I edited the \sent. please
  let me know if it is clear}, we use a heuristic (i.e., the
confidence score from the NLP recommendation model) to select the more
realistic context-aware expanded \sents into \tool{}'s test suite.

@@

For each production of in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and match these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
seed \sent, in their respective positions in the expanded
production.  The left to right traversal of the leaves of an expanded
parse tree forms a masked \sent.  Lastly, we randomly select $k$
masked \sents for the next \sent expansion and validation phase.
\sw{Add justification: why we need to select k masked \sents
  (performance?) and why random makes sense.}

@@

\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked \sent. The \sent ``Or both." is a seed of
\sw{which?} \lc.  The tree on the left shows the
parse tree of this seed; it consists of two productions: ``FRAG->[CC,
  NP, .]" and ``NP->[DT]".  When matching the left-hand-side
non-terminal of the second production (i.e., ``NP") in the reference
CFG, we found that it includes a production ``NP->[DT, NNS]" which has
an additional symbol ``NNS" on the right-hand-side.  The algorithm
thus expands the parse tree with this symbol, shown in the second
tree.  The masked \sent ``Or both \{MASK\}." is the result of the
left-to-right traversal of this expanded parse tree.

@@

In this phase, the words to fill in the masks in the masked \sents
are suggested by the BERT pretrained model \cite{}.  The BERT model
suggests word for the mask symbol

according to its context \sw{what does context mean here?} around in
\sent.  \sw{Algorithm 1 does not require we only have one mask in
  the masked \sent. Can the model suggest multiple words at the
  same time?}  \sw{Say a bit more about the BERT model
  suggestion. E.g., it may suggest multiple words for the same mask
  but they are ranked?}

Because BERT model is not aware of the \lc
specification and the grammar symbol in the expanded parse tree, an
expanded \sent using the suggested words may no longer satisfy the
\lc specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
noun); thus, the suggested word must also be a ``NNS". \sw{Say how we
  obtain the PoS tag of a suggested word.}  Second, we require that
the sentiment of the expanded \sent is the same as the seed
\sent. To ensure this, the suggested words must be \neu.
\sw{Should we present this as part of specification, called expansion
  rule?}  Third, we additionally verify that the expanded \sents
satisfied the same search rules for the seed \sent. Our goal for
generating the expanded \sents is to use them for evaluating the
\sa models on the associated \lc in addition to the seed \sent. It
is only achieved when the expanded \sents are also met with the
same search rules for the \lc. For LC1 as an example, the expanded
\sent must still conform to the specification of the seed's \lc
specification. Therefore, the expanded \sents are required to be
short and to only have \neu adjectives and \nns. \sw{Say why we use
  the third criteria only for LC1 and LC2.}  \jl{I added the
  explanation}

>>>>

The \emph{syntax-based \sent expansion} phase expands the seed
\sents with additional syntactic elements (i.e., words
\sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
syntactic structures ({\bf G2}). It first performs a syntax analysis
to identify the \pos (PoS) tags that can be inserted to each
seed, by comparing the PoS parse trees between the seed \sent and
many other \sents from a large reference dataset. Each identified
tag is inserted into the seed as a \emph{mask}. It then uses an NLP
recommendation model (i.e., BERT \cite{}) to suggest possible
words. If a resulting \sent is validated to be consistent with the
specification which additionally defines the rules for expansion
(e.g., the expanded word should be \neu), {\bf G3} and {\bf G4} are
still satisfied.  Last, because some validated \sents may include
unacceptable suggested words given the context \sw{is this the
  right motivation to do selection?} \jl{I edited the \sent. please
  let me know if it is clear}, we use a heuristic (i.e., the
confidence score from the NLP recommendation model) to select the more
realistic context-aware expanded \sents into \tool{}'s test suite.

@@

For each production of in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and match these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
seed \sent, in their respective positions in the expanded production.
The left to right traversal of the leaves of an expanded parse tree
forms a masked \sent.  Lastly, due to the inefficient cost of
accessing full list of the masked \sents, we randomly select $k$
masked \sents for the next \sent expansion and validation phase when
the masked \sents are more than maximum number of masked \sents. The
random sampling is unbiased approach since it gives same chance to be
chosen. Thus, the random sample becomes representative of the
population of the masked \sents, and it efficiently shows the
usefulness of the \tool.  \sw{Add justification: why we need to select
  k masked \sents (performance?)  and why random makes sense.} \jl{I
  added the statement for it}

@@

\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked \sent. The \sent ``Or both." is a seed of \lc of
\SareqExOne.  The tree on the left shows the parse tree of this seed;
it consists of two productions: ``FRAG->[CC, NP, .]" and ``NP->[DT]".
When matching the left-hand-side non-terminal of the second production
(i.e., ``NP") in the reference CFG, we found that it includes a
production ``NP->[DT, NNS]" which has an additional symbol ``NNS" on
the right-hand-side.  The algorithm thus expands the parse tree with
this symbol, shown in the second tree.  The masked \sent ``Or both
\{MASK\}." is the result of the left-to-right traversal of this
expanded parse tree.

@@

In this phase, the words to fill in the masks in the masked \sents are
suggested by the BERT pretrained model~\cite{devlin2019bert}.  The
BERT is a transformer-based \nl model. It is pretrained on two tasks
of masked token prediction and next sentence prediction. As a result
of the training process, the BERT model suggests word for the mask
token according to its surrounding context in \sent. For each masked
token, multiple words are suggested ranked by their confidence scores.
\sw{Algorithm 1 does not require we only have one mask in the masked
  \sent. Can the model suggest multiple words at the same time?}
\jl{yes. it can predict multiple masked tokens at the same time.}
\sw{Say a bit more about the BERT model suggestion. E.g., it may
  suggest multiple words for the same mask but they are ranked?}
\jl{I added the explanation of BERT}
%
Because BERT model is not aware of the \lc
specification and the grammar symbol in the expanded parse tree, an
expanded \sent using the suggested words may no longer satisfy the
\lc specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
noun); thus, the suggested word must also be a ``NNS". In this work,
we use \spacy, a free open-source library for \nlp, for extracting PoS
tags for each suggested word.\sw{Say how we obtain the PoS tag of a
  suggested word.}\jl{I added it} Second, it is required that the
sentiment of the expanded \sent becomes the same as the seed \sent. To
ensure this, the suggested words must be \neu.  \sw{Should we present
  this as part of specification, called expansion rule?} \jl{I did it
  because I think that there is no issue on mentioning it and that is
  how we assumed and did} Third, we additionally verify that the
expanded \sents satisfied the same search rules for the seed
\sent. Our goal for generating the expanded \sents is to use them for
evaluating the \sa models on the associated \lc in addition to the
seed \sent. It is only achieved when the expanded \sents are also met
with the same search rules for the \lc. For LC1 as an example, the
expanded \sent must still conform to the specification of the seed's
\lc specification. Therefore, the expanded \sents are required to be
short and to only have \neu adjectives and \nns. \sw{Say why we use
  the third criteria only for LC1 and LC2.}  \jl{I added the
  explanation}
